X-ray phase-contrast imaging at \SI{100}{\kilo\electronvolt} on a conventional source

### 2014-03-03 hedpc.tex
cesium iodide
better captions on fig 1/2/3

Here we introduce a method for phase contrast imaging which works on
conventional X-ray sources, covers the entire diagnostic X-ray energy range
and is compatible with compact imaging arrangements. The approach is based
on Talbot-Lau interferometry~\cite{Pfeiffer2006} and employs an edge-on
illumination approach for the grating design and arrangement. Our solution
removes one on the major hurdle which prevented grating interferometry to be
applied at very high X-ray energies so far, namely the fabrication of
gratings with high-aspect ratios. The aspect ratio, given by
\begin{equation} \text{R} = \frac{2h}{p}, \end{equation} where $p$ is the
grating period and $h$ the  structure height, is normally limited by the
fabrication process, usually photolithography~\cite{David2002} or X-ray
lithography~\cite{Mohr2012} as grating structures tend to collapse or deform
(e.g.\ due to capillary forces) if the aspect ratio is too high. For a given
setup length these parameters depend on the target energy $E$ according to
$p \propto 1/\sqrt{E}$ and $h \propto E^3$, and therefore $\textnormal{R}
\propto E^{7/2}$~\cite{Momose2003a}. If at $E=\SI{25}{\kilo\electronvolt}$
an aspect ratio for the absorption grating around $\textnormal{R}=30$ is
necessary for a reasonable length of the experimental arrangement, it would
have to be at least $128$ for $E=\SI{100}{\kilo\electronvolt}$. Moreover,
when using a broad spectrum, photons above the design energy should also be
efficiently blocked by the gratings, which requires even higher aspect
ratios. The largest aspect ratios achieved by current fabrication
techniques~\cite{David2007,Kenntner2010} are around 60.

Our design introduces the edge-on
illuminated,  circularly aligned structures. Edge-on illumination
(Fig.~\ref{Fig:schematic}), as
opposed to face-on illumination, exploits the dimension along the grating
lines to form a high aspect ratio of the structures in the direction of the beam. The
effective structure height of the grating is then determined by the grating
dimension along the grating lines, which essentially allows arbitrarily high
aspect ratios. 
\begin{figure}[h!]
    \centering
    \includegraphics[width=.7\textwidth]{figures/figure1.eps}
    \caption{Schematic of a grating
        interferometer for X-ray energies between 60 and
        \SI{150}{\kilo\electronvolt} in edge-on illumination mode. The
        aspect ratio is defined by the ratio of the travelling distance along the
        grating lines and the period and can be arbitrarily long. In order to maximise
        the field of view, the grating structures are aligned on an
    arc.}%
\label{Fig:schematic}
\end{figure}

@@

Grating design and fabrication is nonstandard and involves a complex mask
design, as shown in Fig.~\ref{Fig:grating_mask}. Multiple gratings can reside on a
silicon chip with their specific structure length and curvature. For the
current experiments, a symmetric interferometer with a grating period of $p
= \SI{2.8}{\micro\metre}$ for all gratings has been used. The design energy
is $\SI{100}{\kilo\electronvolt}$ and the beam splitter grating periodically
shifts the phase by zero and $\pi$ at this energy~\cite{David2002}. Using
gold as the phase shifting material, a structure length of
$h_1 = \SI{19.8}{\micro \metre}$ is required. The analyzer grating is an absorption mask
for sensing slight changes of the interference pattern generated by the beam
splitter~\cite{Momose2003a}. With a structure length of $h_2 =
\SI{800}{\micro \metre}$
it can sufficiently attenuate X-rays up to energies of 
$\SI{160}{\kilo\electronvolt}$. Beam splitter and analyzer grating are
separated at the first fractional Talbot order~\cite{Weitkamp2005},
resulting in an intergrating distance of $\SI{158}{\milli\metre}$. The
source grating splits the relatively large focal spot ($\sim
\SI{1}{\milli\metre}$) into an array of individually coherent, but mutually
incoherent sources~\cite{Pfeiffer2006}. It is also made of gold structures
with a length of $h_0 = h_2 = \SI{800}{\micro \metre}$.
\begin{figure}[h!]
    \centering
    \includegraphics[width=.6\textwidth]{figures/grating_mask.eps}
    \caption{Grating design mask for
        the edge-on illumination approach and \ac{SEM}
        image of the grating. The top part of the 4 inch wafer shows
        five grating chips. The
        gratings have different curvatures which are specific to the grating
        interferometer geometry. 
        The \ac{SEM} image shows the gold structures and the interrupting bridges
        that prevent the lamellae from collapsing~\cite{Kenntner2010}.}\label{Fig:grating_mask}
\end{figure}

@@

Fig.~\ref{Fig:img_chip} shows a radiographic scan of an electronic chip.
Several resistors and an integrated circuits are located on different layers
on the chip. The images were acquired in scanning mode, using a step size of
$\SI{100}{\micro \metre}$ along the $y$ axis. For a better comparison of the
magnified phase and attenuation images, the attenuation image has been
replaced with the differential attenuation image, which was obtained by
digital differentiation. In the attenuation image, the contrast of the soldering points of
the integrated circuit is reduced underneath the resistors, while in
the phase image, they can clearly be identified. The reduced contrast of the 
soldering points in the absorption image is due to beam hardening. The spectrum
impinging on these soldering point is hardened by the resistors in the upper
layer, resulting in lower absorption contrast. Due to the weaker energy
dependency of phase shifts ($1/E$ compared to $1/E^3$), phase-contrast images
are less sensitive to beam hardening~\cite{Chabior2011a}, which explains the
lower contrast reduction of the soldering points underneath the resistors in the
phase image of the chip. This result shows the benefit of the phase contrast in
high-energy X-ray imaging, which may be useful to identify flaws in multilayered
structures such as electronic chips.
\begin{figure}[h!]
    \centering
    \includegraphics[width=.5\textwidth]{figures/img_chip_dabs.eps}
    \caption{Radiographic scan of an electronic chip. The image was acquired
        with 24 phase steps per line and an exposure time of \SI{15}{\second} per
    step. The top right image shows the differential absorption image.}\label{Fig:img_chip}
\end{figure}

@@

The X-ray source is a COMET MXR-160HP/11 X-ray tube with a maximum output
voltage of $\SI{160}{\kilo\volt}$. In the experiment, it was set to the
maximum voltage. The focal spot size is approximately
$\SI{1}{\milli\metre}$. The detector is a CCD camera from Finger Lakes
Instruments. A cesium iodide (CsI:Ti) scintillator of $\SI{600}{\micro
\metre}$ thickness converts the X-rays to visible light and is coupled with
an optical lens projecting the image onto the CCD\@. The effective pixel size
is $\SI{80}{\micro\metre}$. The collimating slit right after the source is 
$\SI{25}{\micro\metre}$ large, while the second slit before the detector is
$\SI{100}{\micro\metre}$.

>>>>

\section*{Results}
Here we introduce a method for phase contrast imaging which works on
conventional X-ray sources, covers the entire diagnostic X-ray energy range
and is compatible with compact imaging arrangements. The approach is based
on Talbot-Lau interferometry~\cite{Pfeiffer2006} and employs an edge-on
illumination approach for the grating design and arrangement. Our solution
removes one on the major hurdle which prevented grating interferometry to be
applied at very high X-ray energies so far, namely the fabrication of
gratings with high-aspect ratios. The aspect ratio, given by
\begin{equation} \text{R} = \frac{2h}{p}, \end{equation} where $p$ is the
grating period and $h$ the  structure height, is normally limited by the
fabrication process, usually photolithography~\cite{David2002} or X-ray
lithography~\cite{Mohr2012} as grating structures tend to collapse or deform
(e.g.\ due to capillary forces) if the aspect ratio is too high. For a given
setup length these parameters depend on the target energy $E$ according to
$p \propto 1/\sqrt{E}$ and $h \propto E^3$, and therefore $\textnormal{R}
\propto E^{7/2}$~\cite{Momose2003a}. If at $E=\SI{25}{\kilo\electronvolt}$
an aspect ratio for the absorption grating around $\textnormal{R}=30$ is
necessary for a reasonable length of the experimental arrangement, it would
have to be at least $128$ for $E=\SI{100}{\kilo\electronvolt}$. Moreover,
when using a broad spectrum, photons above the design energy should also be
efficiently blocked by the gratings, which requires even higher aspect
ratios. The largest aspect ratios achieved by current fabrication
techniques~\cite{David2007,Kenntner2010} are around 60.

Our design introduces the edge-on
illuminated,  circularly aligned structures. Edge-on illumination
(Fig.~\ref{Fig:schematic}), as
opposed to face-on illumination, exploits the dimension along the grating
lines to form a high aspect ratio of the structures in the direction of the beam. The
effective structure height of the grating is then determined by the grating
dimension along the grating lines, which essentially allows arbitrarily high
aspect ratios. 
\begin{figure}[h!]
    \centering
    \includegraphics[width=.7\textwidth]{figures/figure1.eps}
    \caption{Schematic of a grating
        interferometer for X-ray energies between 60 and
        \SI{150}{\kilo\electronvolt} in edge-on illumination mode. The
        aspect ratio is defined by the ratio of the travelling distance along the
        grating lines and the period and can be arbitrarily long. In order to maximise
        the field of view, the grating structures are aligned on an
        arc. A \SI{100}{\kilo\eV} setup was realised where the distance
        between the source and the source grating is \SI{23}{\centi\metre}
    and the distance between the source grating and the phase grating is
    \SI{16}{\centi\metre}. That is also the distance from the phase grating
to the analyzer grating.}%
\label{Fig:schematic}
\end{figure}

@@

Grating design and fabrication is nonstandard and involves a complex mask
design, as shown in Fig.~\ref{Fig:grating_mask}. Multiple gratings can reside on a
silicon chip with their specific structure length and curvature. For the
current experiments, a symmetric interferometer with a grating period of $p
= \SI{2.8}{\micro\metre}$ for all gratings has been used. The design energy
is $\SI{100}{\kilo\electronvolt}$ and the beam splitter grating periodically
shifts the phase by zero and $\pi$ at this energy~\cite{David2002}. Using
gold as the phase shifting material, a structure length of
$h_1 = \SI{19.8}{\micro \metre}$ is required. The analyzer grating is an absorption mask
for sensing slight changes of the interference pattern generated by the beam
splitter~\cite{Momose2003a}. With a structure length of $h_2 =
\SI{800}{\micro \metre}$
it can sufficiently attenuate X-rays up to energies of 
$\SI{160}{\kilo\electronvolt}$. Beam splitter and analyzer grating are
separated at the first fractional Talbot order~\cite{Weitkamp2005},
resulting in an intergrating distance of $\SI{158}{\milli\metre}$. The
source grating splits the relatively large focal spot ($\sim
\SI{1}{\milli\metre}$) into an array of individually coherent, but mutually
incoherent sources~\cite{Pfeiffer2006}. It is also made of gold structures
with a length of $h_0 = h_2 = \SI{800}{\micro \metre}$.
\begin{figure}[h!]
    \centering
    \includegraphics[width=.6\textwidth]{figures/grating_mask.eps}
    \caption{Grating design mask for
        the edge-on illumination approach and \ac{SEM}
        image of the grating. The top part of the 4 inch wafer shows
        five grating chips. From top to bottom, one source grating, two
        phase gratings and two analyzer gratings. The
        gratings have different curvatures which are specific to the grating
        interferometer geometry. 
        The \ac{SEM} image shows the gold structures and the interrupting bridges
        that prevent the lamellae from collapsing~\cite{Kenntner2010}.}\label{Fig:grating_mask}
\end{figure}

@@

\section*{Discussion}
Several resistors and an integrated circuit are located on different layers
on the electronic chip in fig.~\ref{Fig:img_chip}. The radiographs were
acquired in scanning mode, using a step size of
$\SI{100}{\micro \metre}$ along the $y$ axis. For a better comparison of the
magnified phase and attenuation images, the attenuation image has been
replaced with the differential attenuation image, which was obtained by
calculating the derivative along the horizontal axis. In the attenuation
image, the contrast of the soldering points of
the integrated circuit is reduced underneath the resistors, while in
the phase image, they can clearly be identified. The reduced contrast of the 
soldering points in the absorption image is due to beam hardening. The spectrum
impinging on these soldering point is hardened by the resistors in the upper
layer, resulting in lower absorption contrast. Due to the weaker energy
dependency of phase shifts ($1/E$ compared to $1/E^3$), phase-contrast images
are less sensitive to beam hardening~\cite{Chabior2011a}, which explains the
lower contrast reduction of the soldering points underneath the resistors in the
phase image of the chip. This result shows the benefit of the phase contrast in
high-energy X-ray imaging, which may be useful to identify flaws in multilayered
structures such as electronic chips.
\begin{figure}[h!]
    \centering
    \includegraphics[width=.5\textwidth]{figures/img_chip_dabs.eps}
    \caption{Radiographic scan of an electronic chip. The image was acquired
        with 24 phase steps per line and an exposure time of \SI{15}{\second} per
    step. The top right image shows the differential absorption image.}\label{Fig:img_chip}
\end{figure}

@@

The X-ray source is a COMET MXR-160HP/11 X-ray tube with a maximum output
voltage of $\SI{160}{\kilo\volt}$. In the experiment, it was set to the
maximum voltage. The focal spot size is approximately
$\SI{1}{\milli\metre}$. The detector is a CCD camera from Finger Lakes
Instruments. A cesium iodide (CsI:Tl) scintillator of $\SI{600}{\micro
\metre}$ thickness converts the X-rays to visible light and is coupled with
an optical lens projecting the image onto the CCD\@. The effective pixel size
is $\SI{80}{\micro\metre}$. The collimating slit right after the source is 
$\SI{25}{\micro\metre}$ large, while the second slit before the detector is
$\SI{100}{\micro\metre}$.
